### 2025-04-15 cards/paper.tex
starting a cheatsheet written in latex

\documentclass{article}
\usepackage{amsmath,amssymb,amsthm,textcomp}

\title{On Math}
\author{Jacek Walczak}
\date{February - March 2025}

\makeatletter
\newenvironment{leftequation}{%
  \begin{equation}%
    \hspace*{-\displaywidth}%
  }{%
  \end{equation}%
}
\makeatother

\begin{document}

\maketitle

\section{Introduction}
Math content here...

inline math: $x^2 + y^2 = z^2$
display math: \begin{equation}x^2 + y^2 = z^2 \end{equation}

\section{Default symbols}

A - area

\section{Trigonometry}

\begin{equation}
  \begin{gathered}
    \sin\alpha = \frac{\text{opposite}}{\text{hypotenuse}} \\
    \cos\alpha = \frac{\text{adjacent}}{\text{hypotenuse}} \\
    \tan\alpha = \frac{\text{opposite}}{\text{adjacent}} \\
    \csc\alpha = \frac{1}{\sin{\alpha}} =
    \frac{\text{hypotenuse}}{\text{opposite}} \\
    \sec\alpha = \frac{1}{\cos{\alpha}} =
    \frac{\text{hypotenuse}}{\text{adjacent}} \\
    \cot\alpha = \frac{1}{\tan{\alpha}} =
    \frac{\text{adjacent}}{\text{opposite}} \\
  \end{gathered}
\end{equation}

\subsection{Sine values}
\begin{equation}
  \begin{gathered}
    \sin(0°) = 0 \\
    \sin(30°) = \frac{1}{2} \\
    \sin(45°) = \frac{\sqrt{2}}{2} \\
    \sin(60°) = \frac{\sqrt{3}}{2} \\
    \sin(90°) = 1
  \end{gathered}
\end{equation}

\subsection{Cosine values}
\begin{equation}
  \begin{gathered}
    \cos(0°) = 1 \\
    \cos(30°) = \frac{\sqrt{3}}{2} \\
    \cos(45°) = \frac{\sqrt{2}}{2} \\
    \cos(60°) = \frac{1}{2} \\
    \cos(90°) = 0
  \end{gathered}
\end{equation}

% Tangent values

\subsection{Tangent values}
\begin{equation}
  \begin{gathered}
    \tan(0°) = 0 \\
    \tan(30°) = \frac{1}{\sqrt{3}} = \frac{\sqrt{3}}{3} \\
    \tan(45°) = 1 \\
    \tan(60°) = \sqrt{3} \\
    \tan(90°) = \text{undefined}
  \end{gathered}
\end{equation}

\subsection{Formula of a general triangle}

\begin{equation}
  A = \frac{1}{2}ab \sin{C}
\end{equation}
where 'C' (TODO: italize all the 'things') is the measure of the angle between sides 'a' and 'b' (also called 'included angle)

\section{Complex numbers}
\section{Functions}
\subsection{Quadratic formula}
\begin{equation}
  x = \frac{-b \pm \sqrt{b^2 - 4ac}}{2a}
\end{equation}
\subsection{Rational functions}
1. asymptotes
2. roots
\subsection{Exponential functions}
\subsection{Logarithmic functions}
\section{Statistics}
\section{Logarithms}
- product rule
\begin{equation}
\end{equation}

- quotient rule
\begin{equation}
\end{equation}

- power rule
\begin{equation}
\end{equation}

- change of base
\begin{equation}
\end{equation}

- equating arguments
\begin{equation}
\end{equation}

\section{Polynomial identities}
\subsection{Binomial formulas}

\subsection{Cubic formulas}

\end{document}

### 2025-04-15 cards/paper.tex
more and more formulas

@@
 
-\makeatletter
-\newenvironment{leftequation}{%
-  \begin{equation}%
-    \hspace*{-\displaywidth}%
-  }{%
-  \end{equation}%
-}
-\makeatother
-
 \begin{document}
@@
 \maketitle
-
-\section{Introduction}
-Math content here...
-
-inline math: $x^2 + y^2 = z^2$
-display math: \begin{equation}x^2 + y^2 = z^2 \end{equation}
 
@@
   \begin{gathered}
-    \sin\alpha = \frac{\text{opposite}}{\text{hypotenuse}} \\
-    \cos\alpha = \frac{\text{adjacent}}{\text{hypotenuse}} \\
-    \tan\alpha = \frac{\text{opposite}}{\text{adjacent}} \\
-    \csc\alpha = \frac{1}{\sin{\alpha}} =
+    \sin\theta = \frac{\text{opposite}}{\text{hypotenuse}} \\
+    \cos\theta = \frac{\text{adjacent}}{\text{hypotenuse}} \\
+    \tan\theta = \frac{\text{opposite}}{\text{adjacent}} \\
+    \csc\theta = \frac{1}{\sin{\theta}} =
     \frac{\text{hypotenuse}}{\text{opposite}} \\
-    \sec\alpha = \frac{1}{\cos{\alpha}} =
+    \sec\theta = \frac{1}{\cos{\theta}} =
     \frac{\text{hypotenuse}}{\text{adjacent}} \\
-    \cot\alpha = \frac{1}{\tan{\alpha}} =
+    \cot\theta = \frac{1}{\tan{\theta}} =
     \frac{\text{adjacent}}{\text{opposite}} \\
@@
   \begin{gathered}
-    \sin(0°) = 0 \\
-    \sin(30°) = \frac{1}{2} \\
-    \sin(45°) = \frac{\sqrt{2}}{2} \\
-    \sin(60°) = \frac{\sqrt{3}}{2} \\
-    \sin(90°) = 1
+    \sin(0) = 0 \\
+    \sin(30) = \frac{1}{2} \\
+    \sin(45) = \frac{\sqrt{2}}{2} \\
+    \sin(60) = \frac{\sqrt{3}}{2} \\
+    \sin(90) = 1
   \end{gathered}
@@
   \begin{gathered}
-    \cos(0°) = 1 \\
-    \cos(30°) = \frac{\sqrt{3}}{2} \\
-    \cos(45°) = \frac{\sqrt{2}}{2} \\
-    \cos(60°) = \frac{1}{2} \\
-    \cos(90°) = 0
+    \cos(0) = 1 \\
+    \cos(30) = \frac{\sqrt{3}}{2} \\
+    \cos(45) = \frac{\sqrt{2}}{2} \\
+    \cos(60) = \frac{1}{2} \\
+    \cos(90) = 0
   \end{gathered}
@@
   \begin{gathered}
-    \tan(0°) = 0 \\
-    \tan(30°) = \frac{1}{\sqrt{3}} = \frac{\sqrt{3}}{3} \\
-    \tan(45°) = 1 \\
-    \tan(60°) = \sqrt{3} \\
-    \tan(90°) = \text{undefined}
+    \tan(0) = 0 \\
+    \tan(30) = \frac{1}{\sqrt{3}} = \frac{\sqrt{3}}{3} \\
+    \tan(45) = 1 \\
+    \tan(60) = \sqrt{3} \\
+    \tan(90) = \text{undefined}
   \end{gathered}
@@
 \end{equation}
-where 'C' (TODO: italize all the 'things') is the measure of the angle between sides 'a' and 'b' (also called 'included angle)
+where \textit{C} is the measure of the angle between sides \textit{a} and \textit{b} (also called \textit{included angle})
 
 \section{Complex numbers}
+\subsection{Argument of a complex number}
+There is natural angle $\theta$ that \textit{z} makes with real x-axis. This angle is called \textit{the argument of z}. The numeric value of $arg(z)$ is given in radians and also
+\begin{equation}
+0 \leq arg(z) \leq 2\pi
+\end{equation}
+
+Example:
+\begin{equation}
+  \begin{gathered}
+  z = 3 + 4i \\
+  \tan \theta = \frac{4}{3} \\
+  \theta = \arctan\frac{4}{3} \approx 0.93
+  \end{gathered}
+\end{equation}
+
 \section{Functions}
@@
 \end{equation}
+
 \subsection{Rational functions}
-1. asymptotes
-2. roots
+Horizontal asymptotes
+1. Identify the 'dominant term' which is a leading term of the polynomial though we
+usually ugnore the coefficients.
+
+2. Divide every term in the numerator and denominator of $f(x)$ by the dominant term.
+
+3. Evaluate the remaining expression as $x \to \infty$.
+
+Roots
+
+\subsection{Radical function}
+Range of a radical function $f(x) = \sqrt[n]{x}$ depends on index \textit{n} whether it's even or odd.
+
+For odd index like in function $f(x) = -2\sqrt[3]{3x-2}+2$ range is $(-\infty, \infty)$.
+Transformations do not change its range.
+
+For even index $n$ range is $x \geqslant 0$ but the transformations can change the range.
+Horizontal shifts and stretches doesn't change the the range.
+
+For example for function $g(x) = -3\sqrt[4]{2x-1}-2$:
+\begin{equation}
+  \begin{gathered}
+  \sqrt[4]{2x-1} \geqslant 0 \\
+  -3\sqrt[4]{2x-1} \leqslant 0 \\
+  -3\sqrt[4]{2x-1} \leqslant -2 \\
+  g(x) \leqslant -2
+  \end{gathered}
+\end{equation}
+
 \subsection{Exponential functions}
@@
 
+\section{Finite sequences}
+Coefficient rule:
+\begin{equation}
+  \sum_{i=1}^{n} ca_i = c * \sum_{i=1}^{n} a_i
+\end{equation}
+
+Sum rule:
+\begin{equation}
+  \sum_{i=1}^{n} (a_i+b_i) = \sum_{i=1}^{n} a_i + \sum_{i=1}^{n} b_i
+\end{equation}
+
 \section{Polynomial identities}

### 2025-04-15 cards/paper.tex
derivatives and integrals

@@
 
+\section{Geometry}
+\subsection{Rigid motions}
+Or sometimes - any transformations that does not change the distances
+and angles between points in a figure. They are ANGLE-PRESERVING and
+DISTANCE-PRESERVING.
+
+Rigid motions types:
+- translations
+- rotations
+- reflections
+
+Not a rigid motions:
+- dilations
+- stretches
+
 \section{Functions}
@@
 \end{equation}
+
+\subsection{Factor theorem}
+For polynomial, if we know root, we can determine a factor of the
+polynomial. If $p(x)$ is a polynomial and $x=r$ is a root of $p(x)$ then
+\begin{equation}
+  \begin{gathered}
+  p(r) = 0 \\
+  so (x-r) is a factor of p(x) \\
+  generally: (ax-b) is a factor of a polynomial p(x) then \\
+  x = \frac{b}{a} is a root of p(x)
+\end{gathered}
+\end{equation}
+
+\subsection{Inverse functions}
+Inverse functions are denoted by $f^{-1}(x)$.
+
+For $f(x)$ that maps $x=2$ to $y=0$ an inverse function $f^{-1}(x)$ instantiation would be
+$f^{-1}(0)=0$.
+
+Generally it is a simple composition:
+\begin{equation}
+  \begin{gathered}
+    f^{-1}(f(x)) = x \\
+    so \\
+    (f^{-1} \circ f)(x) = x
+  \end{gathered}
+\end{equation}
+
+Calculate inverse function
+1. swap $x$ and $y$
+2. solve for $y$
+
+Example:
+\begin{equation}
+  \begin{gathered}
+    f(x) = 3x-9 \\
+    y = 3x-9 \\
+    x = 3y-9 \\
+    x-3y=-9 \\
+    x+9=3y \\
+    \frac{x+9}{3}=y \\
+    f^{-1}(x)=\frac{x+9}{3}
+  \end{gathered}
+\end{equation}
+
+Domain and range of inverse function:
+Domain of a function $f(x)$ is the range of its inverse function $f^{-1}(x)$.
+Range of a function $f(x)$ is the domain of its inverse function $f^{-1}(x)$.
+
+\subsection{Multiplicities of the roots of a polynomial}
+\begin{equation}
+  p(x) = (x-5)^2(x+8)
+\end{equation}
+for that polynomial roots are $x=5$ and $x=-8$ but factor $(x-5)^2$
+appears TWICE so it is a MULTIPLE ROOT
+$(x+8)$ on the other hand is a SIMPLE ROOT.
 
@@
 
+\section{Derivatives}
+Average rate of change of the function $f(x)$ on the interval $[a, a+h]$
+
+\begin{equation}
+  \frac{\Delta y}{\Delta x} = \frac{f(a+h) - f(a)}{h}
+\end{equation}
+
+Instanteous rate of change of the function at the point $x=a$ is the limit of the average
+rate of change as $h \rightarrow 0$. It's denoted by $f'(a)$ and given by:
+
+\begin{equation}
+  f'(a) = \lim_{h \rightarrow 0}\frac{f(a+h) - f(a)}{h}
+\end{equation}
+
+and its value is equal to the slope of the tangent line to the curve $y = f(x)$ at $x=a$.
+Also it can be defined as:
+\begin{equation}
+  f'(a) = \lim_{x \rightarrow a}\frac{f(x) - f(a)}{x-a}
+\end{equation}
+
+\section{Integrals}
+Also called \textit{antiderivatives}. To represent integrals
+
+Integral of a sum of functions
+\begin{equation}
+  \int f(x) \pm g(x) \, dx = \int f(x) \, dx \pm \int g(x) \, dx
+\end{equation}
+
+Integral of a reciprocal function
+\begin{equation}
+  \int \frac{1}{x} \, dx = \int \ln abs(x) + C
+\end{equation}
+and also:
+\begin{equation}
+  \int \frac{1}{x} \, dx = \int \ln|x| + C = \ln abs(x) + \ln K = \ln (K (abs(x))
+\end{equation}
+
+Integral of an exponential function
+\begin{equation}
+  \int e^x \, dx = e^x + C
+\end{equation}
+with general base we know that
+\begin{equation}
+  \frac{d}{dx} (a^x) = a^x \ln a
+\end{equation}
+so reversing:
+\begin{equation}
+  \int a^x \, dx = \frac{a^x}{\ln a} + C
+\end{equation}
+
+Marked integral for future
+\begin{equation}
+  \int_{a}^{b} f(x) \, dx
+\end{equation}
+
 \end{document}

### 2025-04-22 cards/paper.tex
paper: add logarithms, polynomial identities and linear coefficient

@@
 \section{Statistics}
+\subsection{Linear coefficient}
+Signed with $\rho$ (Greek letter called 'rho').
+- $\rho = 1$ means perfect positive correlation
+- $\rho = -1$ means perfect negative correlation
+- $\rho = 0$ no (linear) correlation
 \section{Logarithms}
-- product rule
+\begin{table}[htbp]
+\centering
+\begin{tabular}{|l|l|}
+\hline
+\textbf{Property} & \textbf{Formula} \\
+\hline
+Product Rule & $\log_a(xy) = \log_a(x) + \log_a(y)$ \\
+\hline
+Quotient Rule & $\log_a\left(\frac{x}{y}\right) = \log_a(x) - \log_a(y)$ \\
+\hline
+Power Rule & $\log_a(x^n) = n \cdot \log_a(x)$ \\
+\hline
+Change of Base & $\log_a(x) = \frac{\log_b(x)}{\log_b(a)}$ \\
+\hline
+Equating arguments & $\log_af(x) = log_ag(x)$ is the same as $f(x) = g(x)$ \\
+\hline
+\end{tabular}
+\caption{Fundamental Properties of Logarithms}
+\label{tab:log_properties}
+\end{table}
+
+% Approach 1: Looser Table with More Spacing
+\begin{table}[htbp]
+\centering
+\renewcommand{\arraystretch}{1.5} % Increases vertical spacing between rows
+\setlength{\tabcolsep}{15pt} % Increases horizontal spacing between columns
+\begin{tabular}{|l|p{5cm}|p{6cm}|}
+\hline
+\textbf{Property} & \textbf{Formula} & \textbf{Description} \\
+\hline
+\textbf{Product Rule} &
+$\log_a(xy) = \log_a(x) + \log_a(y)$ &
+The logarithm of a product equals the sum of the individual logarithms. This transforms multiplication into addition. \\
+\hline
+\textbf{Quotient Rule} &
+$\log_a\left(\frac{x}{y}\right) = \log_a(x) - \log_a(y)$ &
+The logarithm of a quotient equals the difference of logarithms. This transforms division into subtraction. \\
+\hline
+\textbf{Power Rule} &
+$\log_a(x^n) = n \cdot \log_a(x)$ &
+The logarithm of a value raised to a power equals the power multiplied by the logarithm. This transforms exponentiation into multiplication. \\
+\hline
+\textbf{Change of Base} &
+$\log_a(x) = \frac{\log_b(x)}{\log_b(a)}$ &
+This formula allows conversion between different logarithmic bases, useful when calculating logarithms with bases other than those built into calculators. \\
+\hline
+\end{tabular}
+\caption{Fundamental Properties of Logarithms}
+\label{tab:log_properties}
+\end{table}
+
+% Approach 2: List Format with Titles for Each Property
+\section*{Logarithmic Properties}
+
+\subsection*{Product Rule}
 \begin{equation}
+\log_a(xy) = \log_a(x) + \log_a(y)
 \end{equation}
 
-- quotient rule
+The product rule allows us to express the logarithm of a product as the sum of logarithms.
+This is one of the fundamental properties that makes logarithms powerful for simplifying complex calculations.
+When we take the logarithm of a product of two numbers, we can break it down into the sum of the logarithms of each number.
+
+\subsection*{Quotient Rule}
 \begin{equation}
+\log_a\left(\frac{x}{y}\right) = \log_a(x) - \log_a(y)
 \end{equation}
 
-- power rule
+The quotient rule states that the logarithm of a quotient equals the logarithm of the numerator minus the logarithm of the denominator.
+This property transforms division operations into subtraction of logarithms, which is often easier to work with.
+
+\subsection*{Power Rule}
 \begin{equation}
+\log_a(x^n) = n \cdot \log_a(x)
 \end{equation}
 
-- change of base
+The power rule tells us that the logarithm of a number raised to a power equals the power multiplied by the logarithm of the number.
+This property is especially useful when dealing with expressions containing exponents, as it converts exponentiation to multiplication.
+
+\subsection*{Change of Base Formula}
 \begin{equation}
+\log_a(x) = \frac{\log_b(x)}{\log_b(a)}
 \end{equation}
 
-- equating arguments
-\begin{equation}
-\end{equation}
+The change of base formula allows us to convert logarithms from one base to another.
+This is particularly useful in practical applications since most calculators only directly compute natural logarithms (base $e$) and common logarithms (base 10).
+Using this formula, we can express logarithms of any base in terms of logarithms of a different base.
 
@@
 \section{Polynomial identities}
-\subsection{Binomial formulas}
-
-\subsection{Cubic formulas}
+\begin{flalign*}
+& (a + b)^2 = a^2 + 2ab + b^2 & \\
+& (a - b)^2 = a^2 - 2ab + b^2 & \\
+& (a + b)^3 = a^3 + 3a^2b + 3ab^2 + b^3 & \\
+& (a - b)^3 = a^3 - 3a^2b + 3ab^2 - b^3 & \\
+& a^2 - b^2 = (a + b)(a - b) & \\
+& a^3 - b^3 = (a - b)(a^2 + ab + b^2) & \\
+& a^3 + b^3 = (a + b)(a^2 - ab + b^2) &
+\end{flalign*}
 

### 2025-04-22 cards/paper.tex
more updates
- object displacement calculations
- odd and even functions
- functions compositions
- reciprocal functions

@@
 
+\section{Displacement}
+\begin{equation}
+  s = ut+\frac{1}{2}gt^2
+\end{equation}
+where:
+
+$s$ - displacement of the object measured in meters
+
+$u$ - initial velocity of the object measured in meters per second
+
+$t$ - time measured in seconds
+
+$g$ - $9.8\frac{m}{s^2}$ - constant acceleration due to gravity
 \section{Functions}
@@
 \end{equation}
+
+\subsection{Odd and even functions}
+
+Function is said to be odd if:
+\begin{equation}
+  f(-x) = -f(x)
+\end{equation}
+
+Function is said to be even if:
+\begin{equation}
+  f(-x) = f(x)
+\end{equation}
+\subsection{Factor cubics by grouping}
+
+$3x^3-6x^2+2x-4$
+
+1. group them
+
+$(3x^3-6x^2)+(2x-4)$
+
+2. factor larger terms so the leftover match
+
+$3x^2(x-2)+2(x-2)$
+
+3. factor out the binomial
+
+$(3x^2+2)(x-2)$
+
+Note: not all cubics can be factored, however,
+of the cubics that can be factored,
+many can be factored by grouping
 
@@
 
+\subsection{Function composition}
+\begin{equation}
+  (f \circ g)(x) = f(g(x))
+\end{equation}
 \subsection{Inverse functions}
@@
 
+\subsection{Reciprocal functions}
+\begin{equation}
+  f(x) = \frac{1}{x}
+\end{equation}
 \subsection{Exponential functions}

### 2025-04-23 cards/paper.tex
more updates:
- law of sines
- rational roots theorem
- intersection of a reciprocal function and a straight line
- domain of reciprocal transformed function

@@
 \documentclass{article}
-\usepackage{amsmath,amssymb,amsthm,textcomp}
+\usepackage{amsmath,amssymb,amsthm,textcomp,mathtools}
 
@@
 where \textit{C} is the measure of the angle between sides \textit{a} and \textit{b} (also called \textit{included angle})
+
+\subsection{Law of sines}
+% TODO: image needed
+
+\begin{equation}
+  \frac{a}{\sin A} = \frac{b}{\sin B} = \frac{c}{\sin C}
+\end{equation}
+
+and also:
+
+\begin{equation}
+  \frac{\sin A}{a} = \frac{\sin B}{b} = \frac{\sin C}{c}
+\end{equation}
+
+When we have obtuse angle we need to subtract the result from $180$.
 
@@
 
+\subsection{Rational roots theorem}
+Support the rational number $\frac{p}{q}$ in lowest terms, is a root of a polynomial
+with integer coefficient.
+% TODO: add colors to differentiate
+Then 'p' must be the factor of the polynomial's constant term, and 'q' must be a factor
+of its leading coefficient.
+Given a polynomial with integer coefficient, any rational roots of the polynomial must take the
+form:
+\begin{equation}
+  \pm \frac{factor of the constant term}{factor of the leading coefficient}
+\end{equation}
+
+For example:
+\begin{equation}
+  f(x) = 8x^3 + 12x^2 + 6x + 2
+\end{equation}
+so we have 16 possible roots:
+\begin{equation}
+  \begin{gathered}
+    % TODO: strike through
+    \pm \frac{1}{1}, \pm \frac{1}{2}, \pm \frac{1}{4}, \pm \frac{1}{8}, \\
+    \pm \frac{2}{1}, \pm \frac{2}{2}, \pm \frac{2}{4}, \pm \frac{2}{8}
+  \end{gathered}
+\end{equation}
+
+Removing the duplicates, we have 10 possible rational roots:
+\begin{equation}
+  \pm \frac{1}{8}, \pm \frac{1}{4}, \pm \frac{1}{2}, \pm 1, \pm 2
+\end{equation}
+
+Note: it is about 'possible' rational roots.
+
 \subsection{Function composition}
@@
 
+\subsection{Intersection of a reciprocal function and a straight line}
+There are three possibilities when considering the intersection of a reciprocal
+function and a straight line:
+1. there are two intersection points
+2. there is only one intersection point
+3. there are no intersection points at all
+
+% TODO: needs images
+
+Typically, when computing the points of intersection of a reciprocal
+function and a line, we have to solve a system of two equations.
+
+% TODO: needs bracket over two first lines
+\begin{equation}
+  \begin{gathered}
+    y = x \\
+    y = \frac{1}{x} \\
+    x = \frac{1}{x} \\
+    x^2 = 1 \\
+    x = \pm 1
+  \end{gathered}
+\end{equation}
+
 \subsection{Rational functions}
@@
 \end{equation}
+
+% TODO: not range?
+Domain of (transformed) reciprocal function
+\begin{equation}
+f(x) = \frac{a}{bx+c} + d
+\end{equation}
+has the horizontal asymptote $y = d$ therefore the range is
+\begin{equation}
+f(x) = \in (-\infty, d) \cup (d, \infty)
+\end{equation}
+
+% TODO: range
+Range of (transformed) reciprocal function
+\begin{equation}
+f(x) = \frac{a}{bx+c} + d
+\end{equation}
+has the vertical asymptote $y = d$ therefore the range is
+\begin{equation}
+f(x) = \in (-\infty, d) \cup (d, \infty)
+\end{equation}
+
 \subsection{Exponential functions}
@@
 \section{Statistics}
+\subsection{Estimating a mean and variance}
+\subsection{Sum of squares}
 \subsection{Linear coefficient}
@@
 \section{Derivatives}
-Average rate of change of the function $f(x)$ on the interval $[a, a+h]$
+Average rate of change of the function $f(x)$ on the interval $[a, a+h]$:
 
@@
 
+\subsection{Differentiation of an exponent function}
+\begin{equation}
+  \frac{d}{dx} (a^x) = a^x\ln a
+\end{equation}
+with special case:
+\begin{equation}
+  \frac{d}{dx} (e^x) = e^x\ln e = e^x * 1 = e^x
+\end{equation}
+\subsection{Chain rule for exponent function}
+\begin{equation}
+  \begin{gathered}
+    y = e^{3x} \\
+    y = e^u \\
+    u = 3x \\
+    \frac{dy}{dx} = \frac{dy}{du} * \frac{du}{dx} \\
+    \frac{d}{du} e^u = e^u \\
+    \frac{d}{dx} 3x = 3 \\
+    \frac{dy}{dx} = e^u * 3 = 3e^u = 3e^{3x}
+  \end{gathered}
+\end{equation}
+
+\subsection{Derivative of the (natural) logarithm}
+For natural logarithm:
+\begin{equation}
+  \frac{d}{dx}(\ln x) = \frac{1}{x}
+\end{equation}
+
+For general logarithm:
+\begin{equation}
+  \frac{d}{dx}(\log_a x) = \frac{1}{x\ln a}
+\end{equation}
+
+Example with changing base:
+\begin{equation}
+  \begin{gathered}
+  \log_ax = \frac{\ln x}{\ln a}
+  \frac{d}{dx}(\log_ax) = \frac{d}{dx}(\frac{\ln x}{\ln a}) =
+  = \frac{1}{\ln a} * \frac{d}{dx}(\ln x) =
+  = \frac{1}{\ln a} * \frac{1}{x} = \frac{1}{x\ln a}
+  \end{gathered}
+\end{equation}
+\subsection{Chain rule for logarithmic function}
+\begin{equation}
+  \begin{gathered}
+  y = \ln(2x+1)
+  y = \ln u
+  u = 2x+1
+  y' = \frac{1}{u}
+  u' = 2
+  \frac{dy}{dx} = \frac{1}{u} * 2 = \frac{2}{u} = \frac{2}{2x+1}
+  \end{gathered}
+\end{equation}
+
 \section{Integrals}
-Also called \textit{antiderivatives}. To represent integrals
+Also called \textit{antiderivatives}. To represent integrals we use an integral
+symbol.
+
+For example:
+
+\begin{equation}
+  \int 2x dx = x^2 + C
+\end{equation}
+
+Integrals like this are called 'indefinite integrals' and (in this case)
+function being integrated is called an 'integrand'.
 
@@
 
+Power rule for differentiation in reverse:
+\begin{equation}
+  \frac{d}{dx}(x^{n+1}) = (n+1)x^n
+\end{equation}
+same as:
+\begin{equation}
+  \int x^ndx = \frac{x^{n+1}}{n+1}
+\end{equation}
+
+Note: power rule does not work if $n=-1$
+
 Marked integral for future

### 2025-04-24 cards/paper.tex
function graphs and more changes!
- complex numbers - general description, powers of i, magnitude etc
- add couple notes at the beginning
- create a sandbox at the end of the document to save imprtant notes
- couple stylistic changes

@@
 \documentclass{article}
+
 \usepackage{amsmath,amssymb,amsthm,textcomp,mathtools}
+
+\usepackage{tikz}
+\usepackage{pgfplots}
+\pgfplotsset{compat=1.18}
 
@@
 \maketitle
+
+\section{General notes and todos}
+- I feel like multiline equations should have higher vertical spacing
+- Trigonometry values can be done in a single table
 
@@
 \section{Complex numbers}
+Complex numbers can be represented by the point $(x, y)$ where $x$ is real axis and $y$
+is imaginary axis. We call this plane as a 'complex plane', also called 'Argand diagram',
+denoted as $C$.
+
+\subsection{Powers of $i$}
+\begin{equation}
+  \begin{gathered}
+    i^1 = \sqrt{-1} \\
+    i^2 = (\sqrt{-1})^2 = -1 \\
+    i^3 = -1 * i = -i \\
+    i^4 = (-1) * (-1) = 1
+  \end{gathered}
+\end{equation}
+and so on...
+
+\subsection{Magnitude of a complex number}
+The magnitude of a complex number is its distance from the origin $(0, 0)$.
+It is denoted az $|z|$. For complex number $z = a + bi$ magnitude is:
+\begin{equation}
+  |z| = \sqrt{a^2 + b^2}
+\end{equation}
+
 \subsection{Argument of a complex number}
@@
 \subsection{Reciprocal functions}
+
+\begin{figure}
+\centering
+\begin{tikzpicture}
+\begin{axis}[
+    axis lines=center,
+    xlabel=$x$,
+    ylabel=$y$,
+    title={Reciprocal Function $f(x) = \frac{1}{x}$},
+    xmin=-5, xmax=5,
+    ymin=-3, ymax=3,
+    xtick={-5,-4,-3,-2,-1,1,2,3,4,5},
+    ytick={-3,-2,-1,1,2,3},
+    grid=both,
+    domain=-5:5,
+    samples=200,
+    restrict y to domain=-3:3,
+]
+% Plot the function, excluding the region around x=0
+\addplot[blue, thick] {1/x};
+
+% Add asymptotes
+\draw[dashed, red] (axis cs:0,-3) -- (axis cs:0,3);
+\draw[dashed, red] (axis cs:-5,0) -- (axis cs:5,0);
+\end{axis}
+\end{tikzpicture}
+\caption{Graph of the reciprocal function $f(x) = \frac{1}{x}$}
+\end{figure}
+
+%TODO: image
 \begin{equation}
@@
 \end{equation}
-
+When function is not transformed, it passes through points $(-1, -1)$ and $(1, 1)$.
 % TODO: not range?
@@
 \end{equation}
-
 % TODO: range
@@
   \begin{gathered}
-  \log_ax = \frac{\ln x}{\ln a}
-  \frac{d}{dx}(\log_ax) = \frac{d}{dx}(\frac{\ln x}{\ln a}) =
-  = \frac{1}{\ln a} * \frac{d}{dx}(\ln x) =
+  \log_ax = \frac{\ln x}{\ln a} \\
+  \frac{d}{dx}(\log_ax) = \frac{d}{dx}(\frac{\ln x}{\ln a}) = \\
+  = \frac{1}{\ln a} * \frac{d}{dx}(\ln x) = \\
   = \frac{1}{\ln a} * \frac{1}{x} = \frac{1}{x\ln a}
@@
   \begin{gathered}
-  y = \ln(2x+1)
-  y = \ln u
-  u = 2x+1
-  y' = \frac{1}{u}
-  u' = 2
+  y = \ln(2x+1) \\
+  y = \ln u \\
+  u = 2x+1 \\
+  y' = \frac{1}{u} \\
+  u' = 2 \\
   \frac{dy}{dx} = \frac{1}{u} * 2 = \frac{2}{u} = \frac{2}{2x+1}
@@
 Also called \textit{antiderivatives}. To represent integrals we use an integral
-symbol.
-
-For example:
-
+symbol. For example:
 \begin{equation}
@@
 \end{equation}
-
 Integrals like this are called 'indefinite integrals' and (in this case)
@@
 
-Integral of a sum of functions
+\subsection{Integral of a sum of functions}
 \begin{equation}
@@
 
-Integral of a reciprocal function
+\subsection{Integral of a reciprocal function}
 \begin{equation}
@@
 
-Integral of an exponential function
+\subsection{Integral of an exponential function}
 \begin{equation}
@@
 
-Power rule for differentiation in reverse:
+\subsection{Power rule for differentiation in reverse}
 \begin{equation}
@@
 \end{equation}
+Note: power rule does not work if $n=-1$!
 
-Note: power rule does not work if $n=-1$
-
+\section{Sandbox}
 Marked integral for future

### 2025-04-25 cards/paper.tex
updates

@@
 \end{equation}
-
 and also:
-
 \begin{equation}
@@
 \end{equation}
-
 When we have obtuse angle we need to subtract the result from $180$.
@@
 Complex numbers can be represented by the point $(x, y)$ where $x$ is real axis and $y$
-is imaginary axis. We call this plane as a 'complex plane', also called 'Argand diagram',
-denoted as $C$.
+is imaginary axis. We call this plane as a \textbf{complex plane}, also called
+\textit{Argand diagram}, denoted as $C$.
 
@@
 \end{equation}
-
 Example:
@@
 Or sometimes - any transformations that does not change the distances
-and angles between points in a figure. They are ANGLE-PRESERVING and
-DISTANCE-PRESERVING.
+and angles between points in a figure. They are \textbf{angle-preserving} and
+\textbf{distance-preserving}.
 
 Rigid motions types:
+
 - translations
+
 - rotations
+
 - reflections
@@
 Not a rigid motions:
+
 - dilations
+
 - stretches
@@
 \section{Functions}
+\subsection{Standard form}
+\begin{equation}
+  ax + by = c
+\end{equation}
+\subsection{Parallel lines}
+Calculate equation of the parallel line:
+\begin{equation}
+  y - y_1 = m(x - x_1)
+\end{equation}
+Calculate a slope of a line given two points:
+\begin{equation}
+  m = \frac{y_2 - y_1}{x_2 - x_1}
+\end{equation}
 \subsection{Quadratic formula}
@@
 \subsection{Odd and even functions}
-
 Function is said to be odd if:
@@
 \end{equation}
-
 Function is said to be even if:
@@
 \subsection{Factor cubics by grouping}
+For example to factor following function by grouping:
 
-$3x^3-6x^2+2x-4$
-
+\begin{equation}
+  3x^3-6x^2+2x-4
+\end{equation}
 1. group them
-
-$(3x^3-6x^2)+(2x-4)$
-
+\begin{equation}
+  (3x^3-6x^2)+(2x-4)
+\end{equation}
 2. factor larger terms so the leftover match
-
-$3x^2(x-2)+2(x-2)$
-
+\begin{equation}
+  3x^2(x-2)+2(x-2)
+\end{equation}
 3. factor out the binomial
-
-$(3x^2+2)(x-2)$
-
+\begin{equation}
+  (3x^2+2)(x-2)
+\end{equation}
 Note: not all cubics can be factored, however,
@@
 \begin{equation}
-  \begin{gathered}
-  p(r) = 0 \\
-  so (x-r) is a factor of p(x) \\
-  generally: (ax-b) is a factor of a polynomial p(x) then \\
+  p(r) = 0
+\end{equation}
+so $(x-r)$ is a factor of $p(x)$
+generally: $(ax-b)$ is a factor of a polynomial $p(x)$ then:
+\begin{equation}
   x = \frac{b}{a} is a root of p(x)
-\end{gathered}
 \end{equation}
@@
 \end{equation}
-
 For example:
@@
 \end{equation}
-
 Removing the duplicates, we have 10 possible rational roots:
@@
 \end{equation}
-
-Note: it is about 'possible' rational roots.
+Note: it is about \textbf{possible} rational roots.
 
@@
 Inverse functions are denoted by $f^{-1}(x)$.
-
 For $f(x)$ that maps $x=2$ to $y=0$ an inverse function $f^{-1}(x)$ instantiation would be
 $f^{-1}(0)=0$.
-
 Generally it is a simple composition:
 \begin{equation}
-  \begin{gathered}
-    f^{-1}(f(x)) = x \\
-    so \\
+  f^{-1}(f(x)) = x
+\end{equation}
+so
+\begin{equation}
   (f^{-1} \circ f)(x) = x
-  \end{gathered}
 \end{equation}
 
-Calculate inverse function
+Calculate inverse function:
 1. swap $x$ and $y$
+
 2. solve for $y$
@@
 
-Domain and range of inverse function:
 Domain of a function $f(x)$ is the range of its inverse function $f^{-1}(x)$.
+
 Range of a function $f(x)$ is the domain of its inverse function $f^{-1}(x)$.
@@
 for that polynomial roots are $x=5$ and $x=-8$ but factor $(x-5)^2$
-appears TWICE so it is a MULTIPLE ROOT
-$(x+8)$ on the other hand is a SIMPLE ROOT.
+appears \textbf{twice} so it is a \textbf{multiple root}
+$(x+8)$ on the other hand is a \textbf{simple root}.
 
@@
 Horizontal asymptotes
+
 1. Identify the 'dominant term' which is a leading term of the polynomial though we
@@
 \end{equation}
-
 For general logarithm:
@@
 \end{equation}
-
 Example with changing base:

### 2025-04-28 cards/paper.tex
more on statistics
sum of squares note

@@
 \subsection{Logarithmic functions}
+\subsection{Cubic curves functions}
+general function
+\begin{equation}
+  f(x) = ax^3 + bx^2 + cx + d
+\end{equation}
+range:
+\begin{equation}
+  y
+\end{equation}
+
 \section{Statistics}
 \subsection{Estimating a mean and variance}
+\begin{table}[htbp]
+\centering
+\begin{tabular}{|l|l|}
+\hline
+\textbf{Reading times (in minutes)} & \textbf{Frequency} \\
+\hline
+$0 \leqslant x < 20$ & $5$ \\
+\hline
+$20 \leqslant x < 40$ & $10$ \\
+\hline
+$40 \leqslant x < 60$ & $8$ \\
+\hline
+$60 \leqslant x < 80$ & $7$ \\
+\hline
+\end{tabular}
+\caption{Estimating a mean and variance}
+\label{tab:estimating_a_mean_and_variance}
+\end{table}
+To estimate a mean we need a midpoint for $a \leqslant x < b$, so midpoint is $\frac{a+b}{2}$
+\begin{table}[htbp]
+\centering
+\begin{tabular}{|l|l|l|l|}
+\hline
+\textbf{Reading times (in minutes)} & \textbf{Frequency} & \textbf{Midpoint} & \textbf{F*M} \\
+\hline
+$0 \leqslant x < 20$ & $5$ & $10$ & $50$ \\
+\hline
+$20 \leqslant x < 40$ & $10$ & $30$ & $300$ \\
+\hline
+$40 \leqslant x < 60$ & $8$ & $50$ & $400$ \\
+\hline
+$60 \leqslant x < 80$ & $7$ & $70$ & $490$ \\
+\hline
+\end{tabular}
+\caption{Not sure what to type in here}
+\label{tab:estimating_a_mean_and_variance_2}
+\end{table}
+\begin{equation}
+  \overline{\rm x} = \frac{50+300+400+490}{30} = \frac{1240}{30} \approx 41.3
+\end{equation}
+Mean estimation for continous grouped data:
+\begin{equation}
+  \overline{\rm x} \approx \frac{1}{n}\Sigma^K_{i=1}(f_i * m_i)
+\end{equation}
+
+$f_i$ - frequency of the i-th class
+
+$m_i$ - midpoint of the i-th class
+
+$n$ - total number of the observations
+
+Variance estimation
+\begin{equation}
+  \sigma^2_n \approx \frac{1}{n}\Sigma^K_{i=1}(f_i * (m_i - \overline{\rm x})^2)
+\end{equation}
+
+$f_i$ - frequency of the i-th class
+
+$m_i$ - midpoint of the i-th class
+
+$n$ - total number of the observations
+
+$\overline{\rm x}$ - the mean
+
+\begin{table}[htbp]
+\centering
+\begin{tabular}{|l|l|l|l|l|}
+\hline
+\textbf{Midpoint} & \textbf{F*M} & \textbf{$M_i * \overline{\rm x}$} & \textbf{($M_i - \overline{\rm x})^2$} & \textbf{$f_i * (M_i - \overline{\rm x})$} \\
+\hline
+$10$ & $50$ & $-31.333$ & $981.776$ & $4908.879$ \\
+\hline
+$10$ & $30$ & $-11.333$ & $128.444$ & $1284.437$ \\
+\hline
+$50$ & $400$ & $8.667$ & $75.112$ & $600.894$ \\
+\hline
+$70$ & $490$ & $28.667$ & $821.780$ & $5752.458$  \\
+\hline
+\end{tabular}
+\caption{Not sure what to type in here}
+\label{tab:estimating_a_mean_and_variance_3}
+\end{table}
+\begin{equation}
+  \begin{gathered}
+    \sigma^2_n \approx \frac{4908... + 1284... + 600... + 5752}{30} \approx 418.2  \\
+    \sigma_n \approx \sqrt{418.2} \approx 20.5
+  \end{gathered}
+\end{equation}
 \subsection{Sum of squares}
+Given that variance is:
+\begin{equation}
+  \sigma^2_x = \frac{1}{n} \sum_{i=1}^n(x_i - \overline{\rm x})^2
+\end{equation}
+The sum of squares is the same but with no fraction:
+\begin{equation}
+  S_{xx} = \sum_{i=1}^n(x_i - \overline{\rm x})^2
+\end{equation}
+Compare covariance with a sum of squares:
+\begin{equation}
+  \begin{gathered}
+    Cov(x,y) = \frac{1}{n} \sum_{i=1}^n(x_i - \overline{\rm x})(y_i - \overline{\rm y}) \\
+    S_{xy} = \sum_{i=1}^n(x_i - \overline{\rm x})(y_i - \overline{\rm y})
+  \end{gathered}
+\end{equation}
+Variance and covariance in terms of $S_{xx}$, $S_{yy}$ and $S_{xy}$:
+\begin{equation}
+  \begin{gathered}
+    \sigma^2_x = \frac{S_{xx}}{n} \\
+    \sigma^2_y = \frac{S_{yy}}{n} \\
+    Cov(x,y) = \frac{S_{xy}}{n}
+  \end{gathered}
+\end{equation}
+%TODO: some heading?
+Shortcut formulas:
+\begin{equation}
+  \begin{gathered}
+    S_{xx} = \sum_{i=1}^n x_i^2 - \frac{1}{n} (\sum_{i=1}^n x_i)^2 \\
+    S_{yy} = \sum_{i=1}^n y_i^2 - \frac{1}{n} (\sum_{i=1}^n y_i)^2 \\
+    S_{xy} = \sum_{i=1}^n x_iy_i - \frac{1}{n} (\sum_{i=1}^n x_i)(\sum_{i=1}^n y_i)
+  \end{gathered}
+\end{equation}
 \subsection{Linear coefficient}

### 2025-04-28 cards/paper.tex
euler on polyhedrons and linear regression + linear correlation coef

@@
 
+\subsection{Euler on polyhedrons}
+A polyhedron is \textbf{convex} if and only if the following condition
+holds:
+If we take any two distinct points A and B that belong to the polyhedron
+then all the points on the line segment AB also belong to the polyhedron.
+
+Euler's formula for polyhedra for any convex polyhedron, the following
+relationship must be satisfied.
+\begin{equation}
+  V - E + F = 2
+\end{equation}
+
+$V$ - number of vertices
+
+$E$ - number of edges
+
+$F$ - number of faces
+
+The \textbf{Euler characteristic} of any polyhedra is denoted by the
+Greek letter $\aleph$ (``k-eye'') and is equal to the number:
+\begin{equation}
+  \aleph = V - E + F
+\end{equation}
+Any convex polyhedron has
+\begin{equation}
+  \aleph = 2
+\end{equation}
 \section{Displacement}
@@
 \end{equation}
+\subsection{Linear regression}
+For a set of $n$ paired observations $x_i$ and $y_i$ the trend line is the
+straight line that best fits the data.
+Finding the equation of the trend line is called \textbf{linear regression}
+or best fit.
+We can show that the equation of the trend line is given by:
+\begin{equation}
+  y = mx * b
+\end{equation}
+1. Slope $m$
+\begin{equation}
+  m = \frac{S_{xy}}{S_{xx}}
+\end{equation}
+2. y-intercept - b:
+\begin{equation}
+  b = \overline{\rm y} - m\overline{\rm x}
+\end{equation}
+3. $\overline{\rm x}$ and $\overline{\rm y}$ are the means of the data sets:
+\begin{equation}
+  \overline{\rm x} = \frac{1}{n} \sum_{i=1}^nx_i, \overline{\rm y} = \frac{1}{n} \sum_{i=1}^ny_i,
+\end{equation}
+4. quantities $S_{xx}$ and $S_{xy}$:
+\begin{equation}
+  \begin{gathered}
+    S_{xx} = \sum_{i=1}^n (x_i - \overline{\rm x})^2 \\
+    S_{xy} = \sum_{i=1}^n(x_i - \overline{\rm x})(y_i - \overline{\rm y})
+  \end{gathered}
+\end{equation}
+There is some nice intuition behind the formula for $b$. The trend line
+always passes through the point $(\overline{\rm x}, \overline{\rm y})$.
+Therefore, this point must satisfy the trend line equation:
+\begin{equation}
+  y = mx + b
+\end{equation}
+We can then solve this equation for $b$. Also notice that $S_{xx}$ and $S_{xy}$
+are the summation terms that feature in the formulas for the variance and
+covariance respectively.
 \subsection{Linear coefficient}
@@
 - $\rho = 0$ no (linear) correlation
+\subsection{Linear correlation coefficient}
+$|p| > 0.7$ - correlation is strong
+$0.3 \leqslant |p| \leqslant 0.7$ - correlation is weak
+$0 \leqslant |p| \leqslant 0.3$ - correlation is negligible
+\subsection{Linear correlation coefficient using sigma notation}
+\begin{equation}
+  p = \frac{S_{xy}}{\sqrt{S_{xx} * S_{yy}}}
+\end{equation}
 \section{Logarithms}

### 2025-04-29 cards/paper.tex
end behavior of polynomials

@@
 
-%TODO: image
+% TODO: image
 \begin{equation}
@@
 \end{equation}
-%TODO: some heading?
+% TODO: some heading?
 Shortcut formulas:
@@
                           $\log_a(x^n) = n \cdot \log_a(x)$ &
-The logarithm of a value raised to a power equals the power multiplied by the logarithm. This transforms exponentiation into multiplication. \\
+                                                              The logarithm of a value raised to a power equals the power multiplied by the logarithm.
+This transforms exponentiation into multiplication.
+\\
     \hline
@@
                               $\log_a(x) = \frac{\log_b(x)}{\log_b(a)}$ &
-This formula allows conversion between different logarithmic bases, useful when calculating logarithms with bases other than those built into calculators. \\
+                                                                          This formula allows conversion between different logarithmic bases, useful when calculating logarithms with bases other than those built into calculators.
+\\
     \hline
@@
 
-\section{Polynomial identities}
+\section{Polynomials}
+\subsection{Polynomial identities}
 \begin{flalign*}
@@
 \end{flalign*}
-
+\subsection{End behavior of general polynomials}
+Given polynomial
+\begin{equation}
+  f(x) = a_nx^n + a_{n-1}x^{n-1} + ... +a_1x + a_0
+\end{equation}
+with leading coefficient $a \neq 0$ the end behavior is always
+\begin{equation}
+  f(x) \rightarrow \infty
+\end{equation}
+or
+\begin{equation}
+  f(x) \rightarrow -\infty
+\end{equation}
+as
+\begin{equation}
+  x \rightarrow \pm \infty
+\end{equation}
+If the leading coefficient is positive then
+$f(x) \rightarrow \infty$ as $x \rightarrow \infty$,
+if negative then
+$f(x) \rightarrow -\infty$ as $x \rightarrow \infty$
+If leading exponent is \textbf{even}, then the end behavior as $x \rightarrow \infty$ \textbf{is the same} as the end behavior as $x \rightarrow -\infty$.
+Otherwise, if the leading exponent is \textbf{odd}, then the end behavior as $x \rightarrow +\infty$ is the opposite as $x \rightarrow -\infty$.
+\begin{table}[htbp]
+  \centering
+  \begin{tabular}{|l|l|l|l|}
+    \hline
+    \textbf{$n$} & \textbf{$a_n$} & \textbf{$x \rightarrow -\infty$} & \textbf{$x \rightarrow +\infty$} \\
+    \hline
+    even & $>0$ & $f(x) \rightarrow +\infty$ & $f(x) \rightarrow +\infty$ \\
+    \hline
+    even & $<0$ & $f(x) \rightarrow -\infty$ & $f(x) \rightarrow -\infty$ \\
+    \hline
+    odd & $>0$ & $f(x) \rightarrow -\infty$ & $f(x) \rightarrow +\infty$ \\
+    \hline
+    odd & $<0$ & $f(x) \rightarrow +\infty$ & $f(x) \rightarrow -\infty$ \\
+    \hline
+  \end{tabular}
+  \caption{End behavior of polynomials}
+  \label{tab:end_behavior_of_polynomials}
+\end{table}
+Mnemonic trick:
+substitute $+1$ and $-1$ into the leading term of polynomial, for example:
+\begin{equation}
+  \begin{gathered}
+    P(x) = 2x^3 - 6x^2 + 8 \\
+    \\
+    2(+1)^3 = +2 \\
+    P(x) \rightarrow +\infty \\
+    \text{as} \\
+    x \rightarrow +\infty \\
+    \\
+    2(-1)^3 = -2 \\
+    P(x) \rightarrow -\infty \\
+    \text{as} \\
+    x \rightarrow -\infty \\
+  \end{gathered}
+\end{equation}
+In general whenever $n$ is an \textit{even natural number} we have
+\begin{equation}
+  \begin{gathered}
+    \lim_{x \to +\infty}x^n = +\infty \\
+    \text{and} \\
+    \lim_{x \to -\infty}x^n = +\infty
+  \end{gathered}
+\end{equation}
+for $n = 2, 4, 6, ...$ but for \textit{odd natural number} though:
+\begin{equation}
+  \begin{gathered}
+    \lim_{x \to +\infty}x^n = +\infty \\
+    \text{and} \\
+    \lim_{x \to -\infty}x^n = -\infty
+  \end{gathered}
+\end{equation}
+for $n = 1, 3, 5, ...$. To compute the limit at infinity of general polynomial, we only need
+to consider the term with the largest expontent, called the \textbf{leading term}.
+All of the other terms can be disregarded.
+\begin{equation}
+  \begin{gathered}
+    \lim_{x \to \infty}(2x^3 - 7x^2 + 6x + 12) = \\
+    = \lim_{x \to \infty}(2x^3) = \\
+    = \lim_{x \to \infty}(x^3) = \\
+    = \infty
+  \end{gathered}
+\end{equation}
 \section{Derivatives}

### 2025-05-06 cards/paper.tex
law of cosines
more updates:
- graphing cube functions
- normal line functions
- tangent line functions
- chain rule for differentiation

@@
 When we have obtuse angle we need to subtract the result from $180$.
+
+\subsection{Law of cosines}
+% TODO: image needed
+\begin{equation}
+  \begin{gathered}
+    a^2 = b^2 + c^2 - 2bc\cos{A} \\
+    b^2 = a^2 + c^2 - 2ac\cos{B} \\
+    c^2 = a^2 + b^2 - 2ab\cos{C}
+  \end{gathered}
+\end{equation}
 
@@
 \begin{equation}
-  y
+  y \in (-\infty, \infty)
 \end{equation}
+At least one real root and at most three distinct roots. For example:
+\begin{equation}
+  \begin{gathered}
+    y = x^3 - x \\
+    0 = x(x^2 - 1) \\
+    0 = x(x - 1)(x + 1) \\
+    x = -1, 0, 1
+  \end{gathered}
+\end{equation}
+%TODO image
+
+- for single roots, the curve passes through the $x-axis$.
+
+- touches the $x-axis$ and turns around at the double root.
+
+- for root of multiplicity 3, the graph becomes \textit{tangent} (lies parallel) to the $x-axis$ and crosses it.
 
@@
 Average rate of change of the function $f(x)$ on the interval $[a, a+h]$:
-
 \begin{equation}
@@
 \end{equation}
-
 Instanteous rate of change of the function at the point $x=a$ is the limit of the average
 rate of change as $h \rightarrow 0$. It's denoted by $f'(a)$ and given by:
-
 \begin{equation}
@@
 \end{equation}
-
 and its value is equal to the slope of the tangent line to the curve $y = f(x)$ at $x=a$.
@@
 
+\subsection{Tangent line equation}
+% TODO image
+Equation of the tangent line to the curve $y=f(x)$ at the point $P(x_1, y_1)$ is given by
+\begin{equation}
+  \begin{gathered}
+    y - y_1 = m(x - x_1) \\
+    \text{where:} \\
+    m = f'(x_1)
+  \end{gathered}
+\end{equation}
+
+\subsection{Normal line equation}
+% TODO image
+Equation of the normal line to the curve $y=f(x)$ at the point $P(x_1, y_1)$ is given by
+\begin{equation}
+  \begin{gathered}
+    y - y_1 = m(x - x_1) \\
+    \text{where:} \\
+    m = -\frac{1}{f'(x_1)}
+  \end{gathered}
+\end{equation}
+Normal line is just negative reciprocal of the slope of the \textbf{tangent line}.
+
+\subsection{Chain rule for differentiation}
+Derivative of a composite function $f(g(x))$ is given by:
+\begin{equation}
+  \frac{df}{dx} = \frac{df}{dg} * \frac{dg}{dx} = \frac{df}{dx}
+\end{equation}
+Example:
+\begin{equation}
+  \begin{gathered}
+    f(x) = (3x^4 + x^3)^5 \\
+    \frac{df}{dx} = ? \\
+    f = g^5 \\
+    g = 3x^4 + x^3 \\
+    \frac{df}{dx} = \frac{df}{dg} * \frac{dg}{dx} \\
+    \frac{df}{dg} = 5g^4 \\
+    \frac{dg}{dx} = 12x^3 + 3x^2 \\
+    \frac{df}{dx} = 5g^4 * (12x^3 + 3x^2) = 5(3x^4 + x^3)^4(12x^3 + 3x^2)
+  \end{gathered}
+\end{equation}
+The chain rule also can be expressed using primes instead of Leibniz notation
+\begin{equation}
+  f(g(x))' = f'(g(x)) * g'(x)
+\end{equation}
 \subsection{Differentiation of an exponent function}

### 2025-05-14 cards/paper.tex
more and more

@@
 \end{equation}
+\section{Vectors}
+How to call that section?
 \section{Displacement}
@@
 \end{equation}
+\subsection{Residuals and residual plots}
+For dataset of paired numerical observations $(x, y)$ and the corresponding
+linear regression model:
+\begin{equation}
+  \hat y = f(x)
+\end{equation}
+The \textbf{residual} for a particular observation $(x, y)$ is defined as:
+\begin{equation}
+  \begin{gathered}
+    \text{residual} = \text{actual} - \text{estimated} \\
+    y - f(x) = y - \hat y
+  \end{gathered}
+\end{equation}
+We subtract the estimated value predicted by model from the actual observed
+value:
+\begin{itemize}
+\item negative residual - model overestimates the true value
+\item positive residual - model underestimates the true value
+\end{itemize}
+
+Exercises:
+\begin{equation}
+  \begin{gathered}
+    \hat y = 0.02x + 0.8 \\
+    \text{for point} P(400, 8.3) \\
+    \hat y = 0.02 * 400 + 0.8 = 8.8 \\
+    y - \hat y = 8.3 - 8.8 = -0.5
+  \end{gathered}
+\end{equation}
 \section{Logarithms}
@@
 
+\subsection{Second and higher order derivatives}
+The second order derivative is the derivative of a functions first derivative.
+It can be written as $f''(x)$. Also
+\begin{equation}
+  \begin{gathered}
+    f''(x) = (f'(x))' \\
+    \text{example:} \\
+    f(x) = 4x^2 + 3x \\
+    f'(x) = 8x+3 \\
+    f''(x) = 8
+  \end{gathered}
+\end{equation}
+For Leibnitz notation it can be written as:
+\begin{equation}
+  \begin{gathered}
+    f''(x) = \frac{d^2f}{dx^2} = \frac{d}{dx}(\frac{df}{dx}) \\
+    \text{or, for y:} \\
+    \frac{d^2y}{dx^2} \\
+    \text{for higher order, in general:} \\
+    f^{(n)}(x) = \frac{d^n}{dx^n}f(x)
+  \end{gathered}
+\end{equation}
 \section{Integrals}

### 2025-07-02 cards/paper.tex
quotient rule for differentiation
product rule for differentiation
push "integrals of trigonometry functions"
function discontinuity

@@
 
+\subsection{Function continuity}
+If a function $f(x)$ is \textbf{continuous}, we can draw $y = f(x)$ without
+taking our pen off the paper. A function $f(x)$ is continuous at the point
+$x = c$ if:
+
+\begin{equation}
+  \lim_{x \to c}f(x) = f(c)
+\end{equation}
+
+To test for continuity of $f(x)$ we need to check three conditions:
+
+1. does $f(c)$ exists?
+We must check that $f(x)$ is defined at $x=c$
+
+2. does $\lim_{x \to c}f(x)$ exists?
+We must have to check that $\lim_{x \to c^-}f(x) = \lim{x \to c^+}f(x)$
+
+3. does $\lim{x \to c}f(x) = f(c)$
+
+If all of the above is yes, then the function \textbf{is continuous} at $x = c$.
+Otherwise we say there's \textbf{discontinuity} at $x = c$.
+
+\begin{tikzpicture}[scale=1.2]
+    % Draw axes
+    \draw[->] (-0.5,0) -- (5,0) node[right] {$x$};
+    \draw[->] (0,-0.5) -- (0,4) node[above] {$y$};
+
+    % Draw the function curve (looks like a logarithmic or similar curve)
+    % Left part approaching the discontinuity
+    \draw[thick] plot[domain=0.1:5, samples=100] (\x, {1.5 + 0.8*ln(\x)});
+
+    % Mark the discontinuity point
+    \coordinate (c) at (3,0);
+    \coordinate (leftlimit) at (3,2.38);
+
+    % Draw vertical dashed line at x = c
+    \draw[dashed] (3,0) -- (3,3.5);
+
+    % Draw horizontal dashed line showing limit
+    \draw[dashed] (0,2.4) -- (3,2.4);
+
+    % Mark points
+    \fill (leftlimit) circle (2pt);
+
+    % Add labels
+    \node[below] at (3,0) {$c$};
+    \node[left] at (0,2.4) {$\lim_{x \to c}f(x)$};
+    \node[right] at (4.5,2.5) {$y = f(x)$};
+
+    % Add limit annotations
+    \node at (2,0.5) {$x \to c^-$};
+    \node at (4,0.5) {$x \to c^+$};
+
+    % Add arrows showing approach for x
+    \draw[->] (2.5,0.3) -- (2.8,0.3);
+    \draw[->] (3.5,0.3) -- (3.2,0.3);
+
+    % Add arrows showing approach for y
+    \node at (0.5,2.8) {$\downarrow f(x)$};
+    \node at (0.5,2.0) {$\uparrow f(x)$};
+
+\end{tikzpicture}
+
 \section{Statistics}
@@
 \end{equation}
+\subsection{Product rule for differentiation}
+for $f(x) = u(x)*v(x)$ differentiation is:
+\begin{equation}
+  \begin{gathered}
+    f'(x) = u'(x)*v(x) + u(x)*v'(x) \\
+    \text{Using Leibnitz:} \\
+    \frac{dy}{dx} = \frac{du}{dx}*v + \frac{dv}{dx}*u
+  \end{gathered}
+\end{equation}
+\subsection{Quotient rule for differentiation}
+for $f(x) = \frac{u(x)}{v(x)}$ differentiation is:
+\begin{equation}
+  \begin{gathered}
+    f'(x) = \frac{u'(x)*v(x) - u(x)*v'(x)}{[v(x)]^2} \\
+    \text{Using Leibnitz:} \\
+    \frac{d}{dx}(\frac{u}{v}) = \frac{v*\frac{du}{dx} - u*\frac{dv}{dx}}{v^2}
+  \end{gathered}
+\end{equation}
 \subsection{Differentiation of an exponent function}
@@
 
+\subsection{Integrals of trigonometry functions}
+\begin{equation}
+  \begin{gathered}
+    \int \sin x dx = -\cos x + C \\
+    \int \cos x dx = \sin x + C \\
+    \int \sec^2 x dx = \tan x + C \\
+    \int \sec x \tan x dx = \sec x + C \\
+    \int \csc x \cot x dx = -\csc x + C \\
+    \int \csc^2 x dx = -\cot x + C
+  \end{gathered}
+\end{equation}
+
 \subsection{Power rule for differentiation in reverse}

### 2025-08-27 cards/paper.tex
limits in trigonometry functions
upload bunch of topics for future redaction

@@
 \section{Trigonometry}
+-- TODO: properties of a trigonometric functions
+-- like limits, asymptotes etc
+\subsection{Properties of a sine function}
+zeros of the function
+x=n PI
+maxima
+x = pi/2 + 2npi
+minima
+x = -pi/2 + 2npi
+
+sine function is odd (which means it has a rotational symmetry around the origin)
+sin(-x) = -sin(x)
+
+\subsection{Properties of a cosine function}
+\subsection{Properties of a tangent function}
+\subsection{Properties of a cosecant function}
+y = cscx = 1/sinx
+asymptotes: x = n pi
+takes a value of 1 at x = pi/2 2npi
+takes a value of -1 at x = -pi/2 + 2npi
+cosecant is an odd function
+\subsection{Properties of a secant function}
+y = secx = 1/cosx
+asymptotes: x = +- pi/2, +- 3pi/2 etc
+takes a value of 1 at x = 2npi
+takes a value of -1 at x = pi + 2npi
+\subsection{Properties of a cotangent function}
+y = cotx = 1 /tanx = cosx/sinx
+for zeros x = pi/2 + pi n
+vertical asymptotes x = pi n
+period pi
+cotx is an odd function
+
+\subsection{Pythagorean identity}
+\begin{equation}
+  \cos^2(\theta) + \sin^2(\theta) = 1
+\end{equation}
 
@@
 
+\subsection{Limits in trigonometric functions}
+% TODO: image needed
+For sine function:
+\begin{equation}
+  \lim\limits_{x \to a}\sin x = \sin a \\
+  \text{and}
+  \lim\limits_{x \to \pm\infty}\sin x = DNE
+\end{equation}
+
+Similarily for cosine function:
+\begin{equation}
+  \lim\limits_{x \to a}\cos x = \cos a \\
+  \text{and}
+  \lim\limits_{x \to \pm\infty}\cos x = DNE
+\end{equation}
+
+Differently for tangens though:
+\begin{equation}
+  \lim\limits_{x \to a}\tan x = \tan a, a \neq \frac{\pi}{2} + n\pi \\
+  \text{because there function does not exist! but they are infinite at the sides of a vertical asymptote:} \\
+  \lim\limits_{x \to \frac{\pi}{2}^-}\tan x = \infty \\
+  \lim\limits_{x \to \frac{\pi}{2}^+}\tan x = -\infty
+\end{equation}
+
+\subsection{Double angle formula for sine}
+%TODO
+sin(x+y) = sinx cosy + cosx siny
+substituting x = y
+sin2x = 2sinx cosx
+it has many applications, it allows to simplyifying some trigonometric expressions
+and find the exact value for some non-special angles
+this is an identity! not equation, meaning it's true for all xes
+\subsection{Double angle formula for cosine}
+%TODO
+
 \section{Complex numbers}
@@
 How to call that section?
+\subsection{Dot product}
+for vectors a, b and c and scalar lambda
+
+- the dot product distributes over addition:
+(a+b) * c = a*c + b*c
+and
+c*(a+b) = a*c + b*c
+
+- the dot product is associative with respect to scalar multiplication
+(La) * b = L(a*b)
+and
+a*(Lb) = L(a*b)
+
+- the dot product is commutative
+a*b = b*a
+
+- two non-zero vectors a and b are perpendicular if the angle between them is $\theta = 90$
+a perpendicular symbol b
+
+in generat the dot product of two perpendicular vectors is 0. if a perpendicular b and theta is 90 then
+a*b = |a| * |b| * cos90 = |a| * |b| * 0 = 9
+
+if a and b are non-zero vectors you can do a conversion
+a perp b <=> a*b = 0
+
 \section{Displacement}
@@
 
+\subsection{Continuity over an interval}
+In general it is said that function $f(x)$ is continuous over the interval $[a, b]$ if it is:
+
+- continuous on the open interval $(a, b)$
+
+- right continuous at $x = a$
+
+- left continuous at $x = b$
+
+\section{Probability}
+\subsection{Independent events}
+In probability, we say that two events are \textbf{independent} when the outcome of one
+event doesn't influence the outcome of the other event. Otherwise, the events are \textbf{dependent}.
+
+As for multiplication law for independent events:
+\begin{equation}
+  P(A \cap B) = P(A) * P(B)
+\end{equation}
+but, if A and B are independent, then the probability of B occuring is not influenced by
+whether or not A has occured, so:
+\begin{equation}
+  P(B|A) = P(B)
+\end{equation}
+and replacing it for the first law it goes:
+\begin{equation}
+  P(A \cap B) = P(A) * P(B)
+\end{equation}
+
+\subsection{The addition law of probability}
+\begin{equation}
+  P(A \cup B) = P(A) + P(B) - P(A \cap B)
+\end{equation}
+There's some ince intuition behind this law: by adding $P(A)$ to $P(B)$, we count $P(A \cap B)$ twice, hence we need to get rid of one.
+
+\subsection{The multiplication law for conditional probability}
+\begin{equation}
+  P(A|B) = \frac{P(A \cap B)}{P(B)}
+\end{equation}
+% TODO provide an example
+\subsection{The law of total probability}
+% TODO
+
+\section{Series and Sequences}
+It is important to understand the difference between a sequence and a series.
+A sequence is a list of numbers (separated by commmas).
+A series is what you get when you add all of the terms of a sequence together.
+\subsection{The sum of an arithmetic series}
+\begin{equation}
+  S_N = \sum^N_{n=1}a_n
+\end{equation}
+alternatively
+\begin{equation}
+  S_N = \frac{N}{2}(a_1 + a_N)\
+end{equation}
+also, if you don't know the last element of a series, you can use the following:
+\begin{equation}
+  S_N = \frac{N}{2}(a_1 + a_N) = \frac{N}{2}(2a_1 + d(N-1))
+\end{equation}
+
 \section{Statistics}
@@
 \end{equation}
+% TODO
+more accurate I guess:
+\begin{equation}
+  \int \frac{1}{ax+b} \, dx = \frac{1}{a} \ln|ax+b| + C
+\end{equation}
 
@@
 
+\subsection{Left Riemann sum}
+- underestimates the actual area under the curve, if the function is increasing
+
+- overestimates, if the function is decreasing
+
+\subsection{Implicit differentiation}
+%TODO is it a good place?
+
+\subsection{Integrating with substitution}
+%TODO example \int 8(2x+5)^3dx
+general formula
+\begin{equation}
+  \int(ax+b)^n dx = \frac{1}{a(n+1)}(ax+b)^{n+1} + C, n \neq -1
+\end{equation}
+
 \section{Sandbox}

### 2025-08-29 cards/paper.tex
move statistics to new document, prepare doc for linear algebra also

@@
 
-\section{Statistics}
-\subsection{Estimating a mean and variance}
-\begin{table}[htbp]
-  \centering
-  \begin{tabular}{|l|l|}
-    \hline
-    \textbf{Reading times (in minutes)} & \textbf{Frequency} \\
-    \hline
-    $0 \leqslant x < 20$ & $5$ \\
-    \hline
-    $20 \leqslant x < 40$ & $10$ \\
-    \hline
-    $40 \leqslant x < 60$ & $8$ \\
-    \hline
-    $60 \leqslant x < 80$ & $7$ \\
-    \hline
-  \end{tabular}
-  \caption{Estimating a mean and variance}
-  \label{tab:estimating_a_mean_and_variance}
-\end{table}
-To estimate a mean we need a midpoint for $a \leqslant x < b$, so midpoint is $\frac{a+b}{2}$
-\begin{table}[htbp]
-  \centering
-  \begin{tabular}{|l|l|l|l|}
-    \hline
-    \textbf{Reading times (in minutes)} & \textbf{Frequency} & \textbf{Midpoint} & \textbf{F*M} \\
-    \hline
-    $0 \leqslant x < 20$ & $5$ & $10$ & $50$ \\
-    \hline
-    $20 \leqslant x < 40$ & $10$ & $30$ & $300$ \\
-    \hline
-    $40 \leqslant x < 60$ & $8$ & $50$ & $400$ \\
-    \hline
-    $60 \leqslant x < 80$ & $7$ & $70$ & $490$ \\
-    \hline
-  \end{tabular}
-  \caption{Not sure what to type in here}
-  \label{tab:estimating_a_mean_and_variance_2}
-\end{table}
-\begin{equation}
-  \overline{\rm x} = \frac{50+300+400+490}{30} = \frac{1240}{30} \approx 41.3
-\end{equation}
-Mean estimation for continous grouped data:
-\begin{equation}
-  \overline{\rm x} \approx \frac{1}{n}\Sigma^K_{i=1}(f_i * m_i)
-\end{equation}
-
-$f_i$ - frequency of the i-th class
-
-$m_i$ - midpoint of the i-th class
-
-$n$ - total number of the observations
-
-Variance estimation
-\begin{equation}
-  \sigma^2_n \approx \frac{1}{n}\Sigma^K_{i=1}(f_i * (m_i - \overline{\rm x})^2)
-\end{equation}
-
-$f_i$ - frequency of the i-th class
-
-$m_i$ - midpoint of the i-th class
-
-$n$ - total number of the observations
-
-$\overline{\rm x}$ - the mean
-
-\begin{table}[htbp]
-  \centering
-  \begin{tabular}{|l|l|l|l|l|}
-    \hline
-    \textbf{Midpoint} & \textbf{F*M} & \textbf{$M_i * \overline{\rm x}$} & \textbf{($M_i - \overline{\rm x})^2$} & \textbf{$f_i * (M_i - \overline{\rm x})$} \\
-    \hline
-    $10$ & $50$ & $-31.333$ & $981.776$ & $4908.879$ \\
-    \hline
-    $10$ & $30$ & $-11.333$ & $128.444$ & $1284.437$ \\
-    \hline
-    $50$ & $400$ & $8.667$ & $75.112$ & $600.894$ \\
-    \hline
-    $70$ & $490$ & $28.667$ & $821.780$ & $5752.458$  \\
-    \hline
-  \end{tabular}
-  \caption{Not sure what to type in here}
-  \label{tab:estimating_a_mean_and_variance_3}
-\end{table}
-\begin{equation}
-  \begin{gathered}
-    \sigma^2_n \approx \frac{4908... + 1284... + 600... + 5752}{30} \approx 418.2  \\
-    \sigma_n \approx \sqrt{418.2} \approx 20.5
-  \end{gathered}
-\end{equation}
-\subsection{Sum of squares}
-Given that variance is:
-\begin{equation}
-  \sigma^2_x = \frac{1}{n} \sum_{i=1}^n(x_i - \overline{\rm x})^2
-\end{equation}
-The sum of squares is the same but with no fraction:
-\begin{equation}
-  S_{xx} = \sum_{i=1}^n(x_i - \overline{\rm x})^2
-\end{equation}
-Compare covariance with a sum of squares:
-\begin{equation}
-  \begin{gathered}
-    Cov(x,y) = \frac{1}{n} \sum_{i=1}^n(x_i - \overline{\rm x})(y_i - \overline{\rm y}) \\
-    S_{xy} = \sum_{i=1}^n(x_i - \overline{\rm x})(y_i - \overline{\rm y})
-  \end{gathered}
-\end{equation}
-Variance and covariance in terms of $S_{xx}$, $S_{yy}$ and $S_{xy}$:
-\begin{equation}
-  \begin{gathered}
-    \sigma^2_x = \frac{S_{xx}}{n} \\
-    \sigma^2_y = \frac{S_{yy}}{n} \\
-    Cov(x,y) = \frac{S_{xy}}{n}
-  \end{gathered}
-\end{equation}
-% TODO: some heading?
-Shortcut formulas:
-\begin{equation}
-  \begin{gathered}
-    S_{xx} = \sum_{i=1}^n x_i^2 - \frac{1}{n} (\sum_{i=1}^n x_i)^2 \\
-    S_{yy} = \sum_{i=1}^n y_i^2 - \frac{1}{n} (\sum_{i=1}^n y_i)^2 \\
-    S_{xy} = \sum_{i=1}^n x_iy_i - \frac{1}{n} (\sum_{i=1}^n x_i)(\sum_{i=1}^n y_i)
-  \end{gathered}
-\end{equation}
-\subsection{Linear regression}
-For a set of $n$ paired observations $x_i$ and $y_i$ the trend line is the
-straight line that best fits the data.
-Finding the equation of the trend line is called \textbf{linear regression}
-or best fit.
-We can show that the equation of the trend line is given by:
-\begin{equation}
-  y = mx * b
-\end{equation}
-1. Slope $m$
-\begin{equation}
-  m = \frac{S_{xy}}{S_{xx}}
-\end{equation}
-2. y-intercept - b:
-\begin{equation}
-  b = \overline{\rm y} - m\overline{\rm x}
-\end{equation}
-3. $\overline{\rm x}$ and $\overline{\rm y}$ are the means of the data sets:
-\begin{equation}
-  \overline{\rm x} = \frac{1}{n} \sum_{i=1}^nx_i, \overline{\rm y} = \frac{1}{n} \sum_{i=1}^ny_i,
-\end{equation}
-4. quantities $S_{xx}$ and $S_{xy}$:
-\begin{equation}
-  \begin{gathered}
-    S_{xx} = \sum_{i=1}^n (x_i - \overline{\rm x})^2 \\
-    S_{xy} = \sum_{i=1}^n(x_i - \overline{\rm x})(y_i - \overline{\rm y})
-  \end{gathered}
-\end{equation}
-There is some nice intuition behind the formula for $b$. The trend line
-always passes through the point $(\overline{\rm x}, \overline{\rm y})$.
-Therefore, this point must satisfy the trend line equation:
-\begin{equation}
-  y = mx + b
-\end{equation}
-We can then solve this equation for $b$. Also notice that $S_{xx}$ and $S_{xy}$
-are the summation terms that feature in the formulas for the variance and
-covariance respectively.
-\subsection{Linear coefficient}
-Signed with $\rho$ (Greek letter called 'rho').
-- $\rho = 1$ means perfect positive correlation
-- $\rho = -1$ means perfect negative correlation
-- $\rho = 0$ no (linear) correlation
-\subsection{Linear correlation coefficient}
-$|p| > 0.7$ - correlation is strong
-$0.3 \leqslant |p| \leqslant 0.7$ - correlation is weak
-$0 \leqslant |p| \leqslant 0.3$ - correlation is negligible
-\subsection{Linear correlation coefficient using sigma notation}
-\begin{equation}
-  p = \frac{S_{xy}}{\sqrt{S_{xx} * S_{yy}}}
-\end{equation}
-\subsection{Residuals and residual plots}
-For dataset of paired numerical observations $(x, y)$ and the corresponding
-linear regression model:
-\begin{equation}
-  \hat y = f(x)
-\end{equation}
-The \textbf{residual} for a particular observation $(x, y)$ is defined as:
-\begin{equation}
-  \begin{gathered}
-    \text{residual} = \text{actual} - \text{estimated} \\
-    y - f(x) = y - \hat y
-  \end{gathered}
-\end{equation}
-We subtract the estimated value predicted by model from the actual observed
-value:
-\begin{itemize}
-\item negative residual - model overestimates the true value
-\item positive residual - model underestimates the true value
-\end{itemize}
-
-Exercises:
-\begin{equation}
-  \begin{gathered}
-    \hat y = 0.02x + 0.8 \\
-    \text{for point} P(400, 8.3) \\
-    \hat y = 0.02 * 400 + 0.8 = 8.8 \\
-    y - \hat y = 8.3 - 8.8 = -0.5
-  \end{gathered}
-\end{equation}
 \section{Logarithms}
